% ======================================================================
% Section 3.13 -- References & Bibliography
% ======================================================================

All references follow \textbf{IEEE citation style}.

\section{Academic \& Research References}

[1] M. M. Uddin, M. S. Islam, and M. A. Rahman, ``Factors affecting disaster coordination between government and NGOs for relief and rehabilitation activities in Bangladesh,'' \textit{Indian J. Humanities Soc. Sci.}, vol.~2, no.~10, pp.~8--18, 2021.

[2] M. Islam \textit{et al.}, ``Disaster relief and rehabilitation at the local level in Bangladesh: assessing the practices of Union Parishads,'' \textit{J. Disaster Sci. Manage.}, Springer Nature, Jan.~2026.

[3] Harvard Humanitarian Initiative, ``Development, Governance, and Disaster Nexus: Bangladesh Viewpoint,'' 2025. [Online]. Available: \url{https://hhi.harvard.edu}

[4] S. Hossain and M. N. Islam, ``Corruption in cyclone relief and reconstruction: Evidence from a public fund distribution in Bangladesh,'' \textit{J. Development Studies}, Taylor \& Francis, 2025.

[5] M. A. Hossain, ``Disaster management discourse in Bangladesh,'' in \textit{Disaster Management}, InTechOpen, 2013, ch.~4.

[6] UNDRR, ``Bridging national strategy and local action: Bangladesh's success in vertical DRR integration,'' 2025.

[7] M. A. Rahman, M. Hossain, and S. Sultana, ``Disaster management in Bangladesh: Developing an effective emergency supply chain network,'' \textit{Annals of Operations Research}, vol.~283, pp.~1463--1487, 2018.

[8] A. Islam and M. R. Islam, ``Flood hazard assessment and monitoring in Bangladesh,'' \textit{Earth}, vol.~6, no.~3, Aug.~2025.

[9] M. K. Ahmed, ``Towards cyclone resilience: Examining local challenges in shelter management in Southwest Bangladesh,'' \textit{Int. J. Disaster Risk Reduction}, Dec.~2025.

[10] M. A. Uddin, ``Disaster risk reduction in Bangladesh: A comparison of three major floods,'' \textit{Int. J. Disaster Risk Reduction}, vol.~96, Oct.~2023.

\section{Technical References}

[11] MongoDB Inc., ``MongoDB Documentation,'' v8.0. [Online]. Available: \url{https://www.mongodb.com/docs/}

[12] localForage Contributors, ``localForage: Offline Storage Library,'' Mozilla. [Online]. Available: \url{https://localforage.github.io/localForage/}

[13] OpenJS Foundation, ``Node.js Documentation,'' v20 LTS. [Online]. Available: \url{https://nodejs.org/en/docs}

[14] Facebook Inc., ``React Documentation,'' v18. [Online]. Available: \url{https://react.dev}

[15] Vite Contributors, ``Vite Documentation,'' v5.x. [Online]. Available: \url{https://vitejs.dev/guide/}

[16] MongoDB Inc., ``Mongoose ODM Documentation,'' v8.x. [Online]. Available: \url{https://mongoosejs.com/docs/}

[17] M. D. Srinath, ``STRIDE Threat Modeling,'' Microsoft SDL, 2007.

[18] OWASP Foundation, ``OWASP Top Ten 2021.'' [Online]. Available: \url{https://owasp.org/Top10/}

\section{Standards \& Frameworks}

[19] IEEE Std 830-1998, ``IEEE Recommended Practice for Software Requirements Specifications.''

[20] Sendai Framework for Disaster Risk Reduction 2015--2030, UNDRR, 2015.

[21] Government of Bangladesh, ``Disaster Management Act 2012,'' Ministry of Disaster Management and Relief.

[22] Sphere Association, \textit{The Sphere Handbook: Humanitarian Charter and Minimum Standards in Humanitarian Response}, 4th ed., 2018.

[23] V. Agafonkin, ``Leaflet.heat --- Heatmap plugin for Leaflet,'' GitHub.

[24] HeiGIT gGmbH, ``openrouteservice: OpenStreetMap-based routing API.''

[25] Bangladesh Bureau of Statistics, ``Population and Housing Census 2022.''

[26] ADPC and UNDP, ``Comprehensive Disaster Management Programme (CDMP) Bangladesh,'' 2019.

[27] M. B. Hossain and S. Rahman, ``Community-based flood vulnerability assessment in Feni District, Bangladesh,'' \textit{J. Bangladesh Studies}, vol.~24, no.~1, pp.~45--62, 2024.

[28] GeoBoundaries, ``Bangladesh Administrative Boundaries (ADM0--ADM4),'' 2025.
