% ==================================================================
% REFERENCES
% ==================================================================

\begin{thebibliography}{99}

\bibitem{harvard2025}
Harvard Humanitarian Initiative (2025). \textit{Digital Coordination Platforms in Disaster Response}. Harvard University.

\bibitem{sphere2018}
The Sphere Association (2018). \textit{Sphere Handbook: Humanitarian Charter and Minimum Standards in Humanitarian Response}. 4th Edition. Geneva.

\bibitem{bangladesh2024}
Bangladesh Department of Disaster Management (2024). \textit{Flood Situation Report: August 2024}. Government of Bangladesh.

\bibitem{feni2024}
Feni District Administration (2024). \textit{Post-Flood Assessment: Communication Infrastructure Damage}. Government of Bangladesh.

\bibitem{sahana2023}
Sahana Foundation (2023). \textit{Sahana Eden: Humanitarian Information Management Platform}. https://sahanafoundation.org.

\bibitem{hdx2023}
OCHA (2023). \textit{Humanitarian Data Exchange (HDX)}. https://data.humdata.org.

\bibitem{pwa2024}
Google Web Fundamentals (2024). \textit{Progressive Web Apps: Offline-First Architecture}. https://developers.google.com/web/fundamentals.

\bibitem{sandhu1996}
Sandhu, R.S., Coyne, E.J., Feinstein, H.L., and Youman, C.E. (1996). Role-Based Access Control Models. \textit{IEEE Computer}, 29(2), 38--47.

\bibitem{chittagong2023}
Chittagong University Study (2023). \textit{Adequacy of Relief Distribution Process of Union Parishad: A Study on Flood}. Chittagong University.

\bibitem{aila2019}
Post-Cyclone Aila Study (2019). \textit{Household-Level Relief Distribution: Irregularities and Political Influences}. Bangladesh.

\bibitem{ieee8301998}
IEEE (1998). \textit{IEEE Recommended Practice for Software Requirements Specifications}. IEEE Std 830-1998.

\bibitem{mongodb2024}
MongoDB Inc. (2024). \textit{MongoDB Documentation}. https://docs.mongodb.com.

\bibitem{react2024}
Meta (2024). \textit{React Documentation}. https://react.dev.

\bibitem{express2024}
Express.js (2024). \textit{Express.js Documentation}. https://expressjs.com.

\bibitem{localforage2024}
Mozilla (2024). \textit{localforage: Offline Storage, Improved}. https://localforage.github.io/localForage/.

\bibitem{workbox2024}
Google (2024). \textit{Workbox: Service Worker Libraries}. https://developers.google.com/web/tools/workbox.

\bibitem{leaflet2024}
Leaflet (2024). \textit{Leaflet: Open-Source JavaScript Library for Interactive Maps}. https://leafletjs.com.

\bibitem{tailwind2024}
Tailwind Labs (2024). \textit{Tailwind CSS Documentation}. https://tailwindcss.com.

\end{thebibliography}
